---
title: "README-BioMonTools_Shiny"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

```{r, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

# BioMonTools_Shiny
Shiny application for BioMonTools package

# Badges
[![Maintenance](https://img.shields.io/badge/Maintained%3F-yes-green.svg)](https://GitHub.com/leppott/BioMonTools_Shiny/graphs/commit-activity)

[![Lifecycle](https://img.shields.io/badge/lifecycle-stable-green.svg)](https://www.tidyverse.org/lifecycle/#stable)

[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://cran.r-project.org/web/licenses/MIT)

[![GitHub issues](https://img.shields.io/github/issues/leppott//BioMonTools_Shiny.svg)](https://GitHub.com/leppott//BioMonTools_Shiny/issues/)

[![GitHub release](https://img.shields.io/github/release/leppott/BioMonTools_Shiny.svg)](https://GitHub.com/leppott/BioMonTools_Shiny/releases/)
[![Github all releases](https://img.shields.io/github/downloads/leppott/BioMonTools_Shiny/total.svg)](https://GitHub.com/leppott/BioMonTools_Shiny/releases/)

# Installation
To install the current version of the code from GitHub use the example below.

```{r, eval=FALSE}
if(!require(remotes)){install.packages("remotes")}  #install if needed
remotes::install_github("leppott/BioMonTools_Shiny")
```
# Purpose
Provide Shiny interface for BioMonTools package.

# Issues
https://github.com/leppott/BioMonTools_Shiny/issues

# Documentation
None at this time.  Shiny app only.

# Shiny App
A Shiny app is included in the package.

The online version is hosted at 
https://tetratech-wtr-wne.shinyapps.io/BioMonTools

The Shiny app can be run from R console using the shiny package without 
installing the package.

```{r, eval=FALSE}
if(!require(shiny)){install.packages("shiny")}
shiny::runGitHub(repo = "BioMonTools_Shiny"
                , username = "leppott"
                , ref = "main"
                , subdir = "apps/BioMonTools")
```
